HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-22 paper/main.tex
small changes

% UCCA Motivation
The use of UCCA for semantic MT evaluation measure is motivated by two main reasons. 
First, UCCA's foundational layer can
be reliably annotated by non-experts after as little as two hours
of training \parcite{marinotti2014}.
Second, UCCA is cross-linguistically applicable, seeking to
represent what is shared between languages by building on
linguistic typological theory \parcite{Dixon:10a,Dixon:10b,Dixon:12}.
Its cross-linguistic applicability has so far been tested in annotations of
English, French, German and Czech.
Third, the scheme has been shown to be stable across translations:
UCCA annotations of translated text usually contain the same set of relations
\parcite{sulem2015conceptual}, indicating that UCCA reflects a layer of
representation that in a correct translation is mostly shared between
the translation and the source.

@@

In order to validate the HUME metric, we ran an annotation experiment with one source language (English),
and four target languages (Czech, German, Polish and Romanian), using text from the public health domain.
Semantically accurate translation is paramount in this domain, which makes
it particularly suitable for semantic  MT evaluation. HUME is both evaluated in terms of its
consistency (inter-annotator agreement), efficiency (time of annotation) and validity (through a comparison
with crowd-sourced adequacy judgements).

@@

\begin{figure*}[t]
\begin{tabular}{c}
\includegraphics[width=1\textwidth]{tree_653_de1_de2.png}\\
\includegraphics[width=0.6\textwidth]{DAline-extract.png}
\end{tabular}
\caption{An example of a doubly annotated HUME en-de sentence. Structural nodes which are `A' are shown in yellow, and `B' are shown in blue. A sample of 10 of the raw DA assesments for the German machine translation are shown below.}
\label{fig:humeeg}
\end{figure*}
%Original sentence ID = 653
%HUME SID=287
%RAW DA
%82.0+36.0+57.0+32.0+74.0+57.0+24.0+95.0+30.0+0.0+70.0+38.0+41.0+92.0+45.0+15.0+59.0+82.0+24.0+87.0+24.0+24.0+86.0+87.0+8.0+36.0+43.0+61.0+41.0+14.0+0.0+15.0+50.0+16.0+26.0+23.0+83.0+39.0+45.0+1.0+80.0+31.0+53.0+12.0+64.0+22.0+46.0+39.0
%STD DA
%-0.345604136518,-3.33742540772,0.423428930981,-0.548184035933,-0.677176346874,-1.65622648693,-1.55926607798,-1.1272965301,-0.0171653191891,-1.02340816821,-0.872524664699,-0.966670725408,-0.280564543666,-3.14230662916,-0.0830045886964,-1.47697478054,0.470426332641,-1.1678743283,-0.432290259946,-1.92671695959,0.141372817859,-1.36373703007,-0.179200976557,-0.427598369803
%
%54.8 = sample of 10 raw scores
%-0.230 = sample of 10 std scores
%Generate a random sample each time: here is one random sample from score_segs.R: 
%57+64+0+39+83+50+45+53+32+46
%57+64+0+39+83+50+45+53+32+46
%36+64+80+41+1+83+46+50+39+95=535 -> show this one as is closest to 54.8

@@

We have just presented a quantitative comparison between DA and HUME. DA is however, a very
different type of metric to HUME. Looking at Figure~\ref{fig:humeeg} we can see an example of
a German translation annotated with both HUME and DA. DA standardises and averages scores across annotators and returns one score per sentence. 
HUME allows us to interogate the quality of individual types of semantic components in a translation, and in
this sense it is more similar to HMEANT.
Comparing DA and HUME is important in order to see where they agree and to
determine under what circumstances it would be appropriate to apply each method.

@@

HMEANT is a human MT evaluation metric that measures the overlap between the translation a reference
in terms of their SRL annotations.
In this section we present a qualitative comparison between HUME and HMEANT
and the discussion is accompanied by examples from our
experimental data.

@@

\paragraph{Monolingual vs. Bilingual Evaluation.}
\label{src-vs-ref}
HUME diverges from HMEANT and from shallower measures
like BLEU, in not requiring a reference.
Instead, it compares the source directly with the output translation.
This requires the employment of bilingual annotators, but has the benefit of avoiding
using a reference, which is never uniquely defined, and may thus 
lead to unjustly low scores where the translation is a paraphrase of the reference.
If only monolingual annotators are available, the HUME evaluation could be performed
with a reference sentence instead of with the source. This, however,
would risk inaccurate judgements due to the naturally occurring differences
between the source and its reference translations.

@@

All annotation data gathered in this project, together with analysis scripts is available
in github\footnote{\url{https://github.com/bhaddow/hume-emnlp16}}.

>>>>

% UCCA Motivation
The use of UCCA for semantic MT evaluation measure is motivated by two main reasons. 
First, UCCA's foundational layer can be annotated by non-experts after a short training
\parcite{abend2013universal,marinotti2014}.
Second, UCCA is cross-linguistically applicable, seeking to
represent what is shared between languages by building on
linguistic typological theory \parcite{Dixon:10a,Dixon:10b,Dixon:12}.
Its cross-linguistic applicability has so far been tested in annotations of
English, French, German and Czech.
Third, the scheme has been shown to be stable across translations:
UCCA annotations of translated text usually contain the same set of relations
\parcite{sulem2015conceptual}, indicating that UCCA reflects a layer of
representation that in a correct translation is mostly shared between
the translation and the source.

@@

In order to validate the HUME metric, we ran an annotation experiment with one source language (English),
and four target languages (Czech, German, Polish and Romanian), using text from the public health domain.
Semantically accurate translation is paramount in this domain, which makes
it particularly suitable for semantic  MT evaluation. HUME is evaluated in terms of its
consistency (inter-annotator agreement), efficiency (time of annotation) and validity (by comparing it
with crowd-sourced adequacy judgements).

@@

\begin{figure*}[t]
\begin{tabular}{c}
\includegraphics[width=1\textwidth]{tree_653_ver2.png}\\
%\includegraphics[width=0.6\textwidth]{DAline-extract.png}
\end{tabular}
\caption{An example of a doubly annotated HUME en-de sentence. The color of the nodes correspond to their
  HUME label: yellow (A), blue (B), and atomic nodes with their traffic. Nodes in which the annotators
  disagree are split in color. The scale at the bottom right shows a sample of 10 raw DA assessments
  for this example. }
\label{fig:humeeg}
\end{figure*}
%Original sentence ID = 653
%HUME SID=287
%RAW DA
%82.0+36.0+57.0+32.0+74.0+57.0+24.0+95.0+30.0+0.0+70.0+38.0+41.0+92.0+45.0+15.0+59.0+82.0+24.0+87.0+24.0+24.0+86.0+87.0+8.0+36.0+43.0+61.0+41.0+14.0+0.0+15.0+50.0+16.0+26.0+23.0+83.0+39.0+45.0+1.0+80.0+31.0+53.0+12.0+64.0+22.0+46.0+39.0
%STD DA
%-0.345604136518,-3.33742540772,0.423428930981,-0.548184035933,-0.677176346874,-1.65622648693,-1.55926607798,-1.1272965301,-0.0171653191891,-1.02340816821,-0.872524664699,-0.966670725408,-0.280564543666,-3.14230662916,-0.0830045886964,-1.47697478054,0.470426332641,-1.1678743283,-0.432290259946,-1.92671695959,0.141372817859,-1.36373703007,-0.179200976557,-0.427598369803
%
%54.8 = sample of 10 raw scores
%-0.230 = sample of 10 std scores
%Generate a random sample each time: here is one random sample from score_segs.R: 
%57+64+0+39+83+50+45+53+32+46
%57+64+0+39+83+50+45+53+32+46
%36+64+80+41+1+83+46+50+39+95=535 -> show this one as is closest to 54.8

@@

While a quantitative comparison between DA and HUME, as we have just presented, is telling of their
differences and commonalities, it is important to note that the two measures are fundamentally different.
Figure~\ref{fig:humeeg} presents an example of a doubly HUME-annotated English-German example
accompanied by 10 raw DA scores assigned to that sentence. 
While DA standardises and averages scores across annotators to denoise the raw data, and obtain
a single aggregate score, HUME decomposes over a combinatorial structure, thus allowing
to localize the translation errors.
%Comparing DA and HUME is important in order to see where they agree and to
%determine under what circumstances it would be appropriate to apply each method.

@@

HMEANT is a human MT evaluation metric that measures the overlap between the translation a reference
in terms of their SRL annotations.
In this section we present a qualitative comparison between HUME and HMEANT,
using examples from our experimental data.

@@

\paragraph{Monolingual vs. Bilingual Evaluation.}
\label{src-vs-ref}
HUME diverges from HMEANT and from shallower measures
like BLEU, in not requiring a reference.
Instead, it directly compares the source and the translation.
This requires the employment of bilingual annotators, but has the benefit of avoiding
using a reference, which is never uniquely defined, and may thus 
lead to unjustly low scores where the translation is a paraphrase of the reference.
If only monolingual annotators are available, the HUME evaluation could be performed
with a reference sentence instead of with the source. This, however,
would risk inaccurate judgements due to the naturally occurring differences
between the source and its reference translations.

@@

All annotation data gathered in this project, together with analysis scripts is available
online\footnote{\url{https://github.com/bhaddow/hume-emnlp16}}.
